---
title: "Vignette of RDemoPackage"
author: "Johann Posch"
date: "February 10, 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("MASS")
library("RDemoPackage")
library("jsonlite")

```

## R DemoPackage

Demonstrates how to create an R package with dependencies using packrat to include all dependecies. 
For a full description of R package see this documents http://r-pkgs.had.co.nz/

The demo package uses MASS package to demonstrate dependencies.

### Show 'cars' data summary

The cars data set contains two features, speed and distance.

```{r cars}

summary(cars)

```

### Use of RobustLinearRegression in base layer

```{r RobustLinearRegression}

rlmModel = RobustLinearRegression(cars$speed, cars$dist, method="M")
summary(rlmModel)

```

### Use of RobustLinearRegression with JSON 

```{r ExecuteRobustLinearRegression}

    requestJSON = paste0("{\"x\":[4,4,7,7,8,9,10,10,10,11,11,12,12,12,12,13,13,13,13,14,14,14,14,15,15,15,16,16,17,17,17,18,18,18",
                        ",18,19,19,19,20,20,20,20,20,22,23,24,24,24,24,25],\"y\":[2,10,4,22,16,10,18,26,34,17,28,14,20,24,28,26",
                        ",34,34,46,26,36,60,80,20,26,54,32,40,32,40,50,42,56,76,84,36,46,68,32,48,52,56,64,66,54,70,92,93,120,85]}")

    responseJSON = ExecuteRobustLinearRegression(requestJSON)
    res = fromJSON(responseJSON)

    print ("Response from ExecuteRobustLinearRegression : %3f ", res$coefficients )

```


